Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-17 paper.tex
minor fixes

\paragraph{Independent Rules.}
In the last example, part of the stateful algorithm's success stems from the fact that it could reuse a lot of its previous work.
An obvious question is then how well does the stateful algorithm work when there is no work to be reused.

@@

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        title={Depth Test},
        xlabel={Depth},
        ylabel={Time in ms},
        xmin=1, xmax=6,
        ymin=0, ymax=650,
        xtick={1,2,3,4,5,6},
        ytick={2^2,2^4,2^6,2^8},
        ymode=log,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 32.580083) (2, 33.212805) (3, 40.239833) (4, 47.670277) (5, 54.647458) (6, 61.044958) 
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 127.925541) (2, 140.497597) (3, 123.719264) (4, 130.819361) (5, 121.047667) (6, 123.789500)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 108.120444) (2, 107.352694) (3, 116.182833) (4, 125.995639) (5, 137.815527) (6, 142.310597) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 604.595791) (2, 624.541194) (3, 608.671111) (4, 614.285014) (5, 588.636819) (6, 595.276806) 
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Depth benchmark no-precompilation}
    \label{fig:erase-noprecomp}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        title={Depth Test},
        xlabel={Depth},
        %ylabel={Time in ms},
        xmin=1, xmax=6,
        ymin=0, ymax=128,
        xtick={1,2,3,4,5,6},
        ytick={2^1,2^3,2^5,2^7},
        ymode=log,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 12.820514) (2, 12.645666) (3, 17.582138) (4, 22.730528) (5, 27.280097) (6, 32.578722) 
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 13.406416) (2, 13.747139) (3, 12.503764) (4, 12.950486) (5, 12.282083) (6, 12.151930) 
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 83.032819) (2, 79.396889) (3, 85.939180) (4, 92.495542) (5, 96.461291) (6, 105.517458)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 25.681583) (2, 25.322444) (3, 27.672833) (4, 26.999055) (5, 25.690319) (6, 25.257291)
          };
      \end{axis}
    \end{tikzpicture}
    % graph \includegraphics[width=.4\linewidth]{image1}
    \caption{Depth benchmark with precompilation}
    \label{fig:erase-precomp}
  \end{subfigure}
  \caption{The above results depict the behavior of both algorithms in depending on the \text{depth} of potential partial matches. The lines with square entry points represent problems where unification is easy. The lines with circle entry points are the same tests with hard unification problems.}
  \label{fig:erase}
  \end{figure}

>>>>

\paragraph{Independent Rules.}
In the last example, part of the stateful algorithm's success stems from the fact that it could reuse a lot of its previous work.
An obvious question is then how well does the stateful algorithm behave when there is no work to be reused.

@@

\begin{figure}
  \centering
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        title={Depth Test},
        xlabel={Depth},
        ylabel={Time in ms},
        xmin=1, xmax=6,
        ymin=0, ymax=2^10,
        xtick={1,2,3,4,5,6},
        ytick={4,16,64,256,1024},
        ymode=log,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 32.580083) (2, 33.212805) (3, 40.239833) (4, 47.670277) (5, 54.647458) (6, 61.044958) 
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 127.925541) (2, 140.497597) (3, 123.719264) (4, 130.819361) (5, 121.047667) (6, 123.789500)
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 108.120444) (2, 107.352694) (3, 116.182833) (4, 125.995639) (5, 137.815527) (6, 142.310597) 
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 604.595791) (2, 624.541194) (3, 608.671111) (4, 614.285014) (5, 588.636819) (6, 595.276806) 
          };
      \end{axis}
    \end{tikzpicture}
    \caption{Depth benchmark no-precompilation}
    \label{fig:erase-noprecomp}
  \end{subfigure}%
  \begin{subfigure}{.5\textwidth}
    \centering
    \begin{tikzpicture}[scale=0.75]
      \begin{axis}[
        title={Depth Test},
        xlabel={Depth},
        %ylabel={Time in ms},
        xmin=1, xmax=6,
        ymin=0, ymax=170,
        xtick={1,2,3,4,5,6},
        ytick={2^1,2^3,2^5,2^7},
        ymode=log,
        log basis y=2,
        legend pos=north west,
        ymajorgrids=true,
        grid style=dashed,
        legend image post style={mark=},
        ]
        \addplot[
          color=orange,
          mark=square,
          ]
          coordinates {
            (1, 12.820514) (2, 12.645666) (3, 17.582138) (4, 22.730528) (5, 27.280097) (6, 32.578722) 
          };
        \addlegendentry{naive}
        \addplot[
          color=blue,
          mark=square,
          ]
          coordinates {
            (1, 13.406416) (2, 13.747139) (3, 12.503764) (4, 12.950486) (5, 12.282083) (6, 12.151930) 
          };
        \addlegendentry{incremental}
        \addplot[
          color=orange,
          mark=o,
          ]
          coordinates {
            (1, 83.032819) (2, 79.396889) (3, 85.939180) (4, 92.495542) (5, 96.461291) (6, 105.517458)
          };
        \addplot[
          color=blue,
          mark=o,
          ]
          coordinates {
            (1, 25.681583) (2, 25.322444) (3, 27.672833) (4, 26.999055) (5, 25.690319) (6, 25.257291)
          };
      \end{axis}
    \end{tikzpicture}
    % graph \includegraphics[width=.4\linewidth]{image1}
    \caption{Depth benchmark with precompilation}
    \label{fig:erase-precomp}
  \end{subfigure}
  \caption{The above results depict the behavior of both algorithms in depending on the \text{depth} of potential partial matches. The lines with square entry points represent problems where unification is easy. The lines with circle entry points are the same tests with hard unification problems.}
  \label{fig:erase}
  \end{figure}
